Tidy Amicus Data

### 2022-01-25 data-cleaning/00-scrape-amicus-text.Rmd
add intro phrase checks

@@

```{r}
box_write(amicus_txt,
          file_name = "shortened-amicus-brief-text.csv",
          dir_id = '145990409196')
```

>>>>

Check that our files contain "summary of (the) argument: this is the phrase that indicates the start of the text we want to analyze.

```{r}
amicus_txt %>% 
  mutate(txt_full = str_squish(txt_full),
         summary = grepl("summary of argument|summary of the argument", txt_full, ignore.case = T)) %>%
  group_by(summary) %>% 
  summarize(n=n())
```

Which files do not? -- should just be the 3 that we have manual adjustments recorded for.

```{r}
amicus_txt %>% 
  mutate(txt_full = str_squish(txt_full),
         summary = grepl("summary of argument|summary of the argument", txt_full, ignore.case = T)) %>%
  filter(!summary) %>% 
  select(brief)
```

Final column names

```{r}
amicus_txt %>% colnames()
```

@@

```{r}
box_write(amicus_txt,
          file_name = "raw-amicus-brief-text.csv",
          dir_id = '145990409196')
```
